Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-10 ms.Rmd
Fancy new figure 1 and updated MS.

```{r Figure1, fig.width = 14, fig.height= 14, fig.cap= "Chromatic and achromatic contrast in Just Noticiable Differences (JND), of Hawaiian and Kenyan chameleons against their respective backgrounds (i.e., average environment of stems and leaves). A & B) Contrast of male chameleons during male-male contests and courtship. JNDs are calculated based on the chameleon visual system. NS denotes non-significant contasts, whereas astericks indicates significant differences is < 0.001."}
rerun = FALSE
if(rerun){
## Make figures that average across body regions, but display Social Context

@@

### Supplementary Tables - Add to Supplement. Easier to generate here given all code is here.

# Social context. We only need models because contarsts are already there

@@

 # Table
table1 <- flextable(final_T1) %>% table_style6()

table1
```

# Predators - Models AND contrasts. We don't get all contrasts because we have two factors in model
```{r table2, fig.width = 8, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards for snakes and lizards. Full models are provided and standard errors are corrected by using robust variance estimators."}

@@

# Clean
 final_T2 <- table2 %>% 
             mutate(JND = c("Achromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3))) %>%
              select(JND, Parameter, beta, SE, df, CI_L, CI_U)
 write.csv(final_T2, file = "./output/tables/Table2_MS.csv", row.names = FALSE)
 # Table
table2 <- flextable(final_T2) %>%
           table_style7()

table2
```

@@

table3 <- flextable(contrast) %>% table_style8()
table3
```

# Local Adaptation. We have all the contrasts we need from the model because we are only comparing Hawaii-Hawaii(background) to Hawaii-Kenya(background). These are therefore in the table output already.

@@

write.csv(tb4, file = "./output/tables/Table4_MS.csv", row.names = FALSE)
table4 <- flextable(tb4) %>% table_style9()
table4
```

>>>>

```{r Figure1, fig.width = 14, fig.height= 14, fig.cap= "Chromatic and achromatic contrast in Just Noticiable Differences (JND), of Hawaiian and Kenyan chameleons against their respective backgrounds (i.e., average environment of stems and leaves). A & B) Contrast of male chameleons during male-male contests and courtship. JNDs are calculated based on the chameleon visual system. NS denotes non-significant contasts, whereas astericks indicates significant differences is < 0.001. Insets showing spectral reflectance curves of two representative body regions ('gular' and 'top-flank), along with average signalling background (averaged leaves) are provided for each social and predatory context. A) spectral curves of signals during male-male displays; B) spectral curves of signals during courtship displays; C) spectral curves of signals during bird encounters; and D) spectral curves of signals during snake encounters."}
rerun = FALSE
if(rerun){
## Make figures that average across body regions, but display Social Context

@@

@@

```{r table2, fig.width = 8, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards for snakes and lizards. Full models are provided and standard errors are corrected by using robust variance estimators."}

@@

# Clean
 final_T2 <- table2 %>% 
             mutate(JND = c("Achromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3))) %>%
              select(JND, Parameter, beta, SE, df, CI_L, CI_U)
 write.csv(final_T2, file = "./output/tables/Table2_MS.csv", row.names = FALSE)

@@

@@

write.csv(tb4, file = "./output/tables/Table4_MS.csv", row.names = FALSE)
